Best practices for forecasting changes in biodiversity: an example using breeding birds

### 2017-09-05 manuscript/draft.Rmd
variance partitioning

Partitioning each model's squared error into consistent errors across sites and
errors that fluctuated year-to-year shows that the majority of the error comes
from errors in the site-level mean (Figure 6). The "average" model, which was
based on the site-level mean, had the lowest error in this regard. In contrast,
the three environmental models showed the largest biases at the site level; this
makes sense, given that they could not explicitly distinguish among sites with
similar climate, NDVI, and elevation.

>>>>

Partitioning each model's squared error shows that the majority of the residual
error was attributed to errors in estimating site-level means, rather than
errors in tracking year-to-year fluctuations (Figure 6). The "average" model,
which was based entirely on site-level means, had the lowest error in this
regard. In contrast, the three environmental models showed larger biases at the
site level, though they still explained most of the variance in this component.
This makes sense, given that they could not explicitly distinguish among sites
with similar climate, NDVI, and elevation. Interestingly, the environmental
models had higher squared error than the baselines did for tracking year-to-year
fluctuations in richness as well.
